Integrating Common Ground and Informativeness in Pragmatic Word Learning

### 2019-01-29 papers/cogsci2019/cogsci2019.Rmd
add saves to cogsci folder

pred_ex3 <- readRDS(file = "../../stats/saves/model_predictions_ex3_1.rds")

pred_ex4 <- readRDS(file = "../../stats/saves/model_predictions_ex3_variable_priors.rds")

bf_ex3 <- readRDS(file = "../../stats/saves/ex3_bf.rds")

bf_ex4 <- readRDS(file = "../../stats/saves/ex4_bf.rds")

>>>>

pred_ex3 <- readRDS(file = "saves/model_predictions_ex3_1.rds")

pred_ex4 <- readRDS(file = "stats/saves/model_predictions_ex3_variable_priors.rds")

bf_ex3 <- readRDS(file = "stats/saves/ex3_bf.rds")

bf_ex4 <- readRDS(file = "stats/saves/ex4_bf.rds")
